Ice sheet mass flows

### 2025-08-21 sankey.tex
Change figure ratio

      \ifnum \numexpr\Q{vFRONTRET} > 0
        \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET},
          at={[yshift=-\yoff]SHELFMELT.right}}
        \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET},
          at={[yshift=-\yoff]SHELFMELTa.right}, anchor=left}
      \fi
      \sankeynode{name=CALVa, quantity=\qq{CALV},
        at={[yshift=\yoff,xshift=0mm]SHELFMELTa.left}, anchor=right}
    }

@@

    %% \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET}, at={[yshift=-\yoff]SHELFMELTa.right}}
    \ifthenelse{\Q{vFRONTRET} > 0} {
      \sankeyoutin[out-blue]{FRONTRET}{FRONTRETa};
      \sankeynode{name=GZa, quantity=\qq{GZ}, at={[yshift=-\yoff]FRONTRETa.right}, anchor=left}
      \sankeyadvance[out-blue]{FRONTRETa}{10mm}; 
      \sankeyend[out-blue]{FRONTRETa}; \labelright{FRONTRETa}{vFRONTRET}
    } {
      \sankeynode{name=GZa, quantity=\qq{GZ}, at={[xshift=-10mm,yshift=-\yoff]SHELFMELTa.right}, anchor=left}
    }

@@

    \sankeyoutin[ice-to-water]{GZ}{GZa}; \sankeyadvance[water]{GZa}{10mm};
    \sankeyend[water]{GZa}; \labelright{GZa}{vGZRET}

>>>>

      \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET},
        at={[yshift=-\yoff]SHELFMELT.right}}
      \sankeynode{name=CALVa, quantity=\qq{CALV},
        at={[yshift=\yoff,xshift=0mm]SHELFMELTa.left}, anchor=right}
      \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET},
        at={[yshift=-\yoff]SHELFMELTa.right}, anchor=left}
    }

@@

    %% \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET}, at={[yshift=-\yoff]SHELFMELTa.right}}
    \sankeyoutin[out-blue]{FRONTRET}{FRONTRETa};

    \sankeynode{name=GZa, quantity=\qq{GZ}, at={[yshift=-\yoff]FRONTRETa.right}, anchor=left}

@@

    \sankeyoutin[ice-to-water]{GZ}{GZa}; \sankeyadvance[water]{GZa}{10mm};
    \sankeyend[water]{GZa}; \labelright{GZa}{vGZRET}
    \sankeyadvance[out-blue]{FRONTRETa}{10mm}; 
    \sankeyend[out-blue]{FRONTRETa}; \labelright{FRONTRETa}{vFRONTRET}
